\begin{longtable}{|c| l| l | >{\centering\arraybackslash}p{3cm} | l| }
\caption{Taxonomic groupings of phytoplasmas \cite{p13}} \label{AllPhy}\\ \hline
16Sr group & Candidatus species & Type strain & GenBank 

accession number & Geographic distribution of the group \\ \hline \hline
I-A & Candidatus Phytoplasma asteris & Aster yellows witches' broom & NC\_007716 & North America, Europe\\ \hline
I-B & Ca. Phytoplasma asteris& Onion yellows& NC\_005303 &Worldwide \\ \hline
I-C & Ca. Phytoplasma asteris &Clover phyllody & AF222065 & North America, Europe \\ \hline
I-D & Ca. Phytoplasma asteris & Paulownia witches' broom & AY265206 & Asia \\ \hline
I-E & Ca. Phytoplasma asteris & Blueberry stunt & AY265213 & North America \\ \hline
I-F & Ca. Phytoplasma asteris & Apricot chlorotic leaf roll & AY265211 & Spain \\ \hline
II-A & & Peanut witches' broom &L33765 &Asia \\ \hline
II-B & Ca. Phytoplasma aurantifolia & Lime witches' broom & U15442 & Arabian peninsula \\ \hline
II-C & & Cactus witches' broom & AJ293216 & Asia, Africa \\ \hline
II-D & Ca. Phytoplasma australasiae & Papaya yellow crinkle & Y10097 & Australia \\ \hline
III-A & Ca. Phytoplasma pruni & Western X disease & L04682 & North America \\ \hline
III-B & & Clover yellow edge & AF189288 & America, Asia, Europe \\ \hline
IV-A & Ca. Phytoplasma palmae & Coconut lethal yellowing & AF498307 & Florida, Caribbean  \\ \hline
IV-B & Ca. Phytoplasma palmae & Phytoplasma sp.LfY5(PE65)-Oaxaca & AF500334 & Mexico  \\ \hline
IV-D & Ca. Phytoplasma palmae & Carludovica palmata leaf yellowing & AF237615 & Mexico  \\ \hline
V-A & Ca. Phytoplasma ulmi & Elm yellows & AY197655 & North America, Europe \\ \hline
V-B & Ca. Phytoplasma ziziphi & Jujube witches' broom & AB052876 & Asia  \\ \hline
V-C & Ca. Phytoplasma vitis & Alder yellows & AY197642 & Europe \\ \hline
V-G & & Jujube witches' broom related & AB052879 & Asia  \\ \hline
VI-A & Ca. Phytoplasma trifolii & Clover proliferation & AY390261 & North America, Asia \\ \hline
VII-A & Ca. Phytoplasma fraxini & Ash yellows & AF092209 & North America  \\ \hline
VIII-A & Ca. Phytoplasma luffae & Loofah witches'  broom & AF353090 & Taiwan \\ \hline
IX-A & & Pigeon-pea witches' Broom & AF248957 & America \\ \hline
IX-D & Ca. Phytoplasma phoenicium & Almond witches'  broom & AF515636 & Middle East \\ \hline
X-A & Ca. Phytoplasma mali & Apple proliferation & AJ542541 & Europe  \\ \hline
X-C & Ca. Phytoplasma pyri & Pear decline & AJ542543 & Europe \\ \hline
X-D & Ca. Phytoplasma spartii  & Spartium witches' broom &  X92869 &  Europe \\ \hline
X-F & Ca. Phytoplasma prunorum & European stone fruit yellows & AJ542544 & Europe \\ \hline
XI-A & Ca. Phytoplasma oryzae &  Rice yellow dwarf & AB052873&  Asia, Africa, Europe  \\ \hline
XII-A & Ca. Phytoplasma solani &  Stolbur & AJ964960 & Europe \\ \hline
XII-B & Ca. Phytoplasma australiense & Australian grapevine yellows& L76865& Australasia \\ \hline
XII-C &&Strawberry lethal yellows &AJ243045& Australia \\ \hline
XII-D &Ca. Phytoplasma japonicum& Japanese hydrangea phyllody& AB010425 &Japan \\ \hline
XII-E &Ca. Phytoplasma fragariae& Strawberry yellows &DQ086423& Europe \\ \hline
XIII-A && Mexican periwinkle virescence& AF248960 &Mexico, Florida \\ \hline
XIV-A &Ca. Phytoplasma cynodontis& Bermudagrass whiteleaf &AJ550984 &Asia, Africa \\ \hline
XV-A  & Ca. Phytoplasma brasiliense& Hibiscus witches' broom& AF147708& Brazil \\ \hline
XVI-A & Ca. Phytoplasma graminis & Sugar cane yellow leaf &AY725228 &Cuba \\ \hline
XVII-A &Ca. Phytoplasma caricae &Papaya bunchy top &AY725234& Cuba \\ \hline
XVIII-A &Ca. Phytoplasma americanum& Potato purple top wilt &DQ174122 &North America \\ \hline
XIX-A &Ca. Phytoplasma castanae & Chestnut witches' broom &AB054986& Japan \\ \hline
XX-A &Ca. Phytoplasma rhamni &Buckthorn witches' broom& X76431 &Germany \\ \hline
XXI-A& Ca. Phytoplasma pini &Pine shoot proliferation &AJ632155 &Spain \\ \hline
XXII-A &Ca. Phytoplasma cocosnigeriae & Coconut lethal decline &Y14175& West Africa, Mozambique \\ \hline
XXIII-A & &Buckland valley grapevine yellows& AY083605& Australia \\ \hline
XXIV-A&& Sorghum bunchy shoot& AF509322 &Australia \\ \hline
XXV-A&& Weeping tea witches' broom& AF521672& Australia \\ \hline
XXVI-A &&Sugar cane phytoplasma D3T1& AJ539179& Mauritius \\ \hline
XXVII-A&& Sugar cane phytoplasma D3T2& AJ539180 &Mauritius \\ \hline
XXVIII-A && Derbid phytoplasma&AY744945& Cuba \\ \hline
XXIX-A & Ca. Phytoplasma allocasuarinae&  Allocasuarina muelleriana phytoplasma& AY135523& Australia \\ \hline
XXX-A& Ca. Phytoplasma cocostanzaniae & Tanzanian lethal decline& X80117& Tanzania \\ \hline
\end{longtable} 